\begin{problem}{shirts}{standard input}{standard output}{1.5 seconds}{256 megabytes}

The trainers of December Course 2024 are arranging participants into $N$ groups, numbered $1$ to $N$, placed in a row. For simplicity, each participant in group $i$ initially wears a shirt of color $i$.

The trainers can issue commands to modify group shirt colors or check specific color statistics. They provide $Q$ commands in total, which must be processed in the given order. Commands are of the following two types:

\begin{itemize}
\item $1\ x\ c$: Change the shirt color of trainee $x$ and all connected trainees (trainees reachable by moving through adjacent groups with the same shirt color) to color $c$.

\item $2\ c$: Report how many trainees are currently wearing shirts of color $c$.
\end{itemize}

\InputFile
The first line of input contains two integers, $N$ and $Q$

Then follows $Q$ lines, each describing a query.

Each query is in one of the following formats:

\begin{itemize}
\item $1\ x\ c$

\item $2\ c$
\end{itemize}

as described above.

\OutputFile
Let $q$ be the number of type $2$ queries. 

Print $q$ lines, where the $i$-th line contains the answer to the $i$-th type $2$ query.

\Scoring
For all testcases it is guaranteed that

\begin{itemize}
\item $1 \leq N, Q \leq 3 \times 10^5$

\item $1 \leq x, c \leq N$

\item There is at least one query of type $2$.

\item All input values are integers.
\end{itemize}

\begin{center}
\begin{tabular}{|c|c|c|} 
\hline
\textbf{Subtask} & \textbf{Score} & \textbf{Additional constraints} \\
\hline
1 & 10 & There will be no queries of type 1. \\
\hline
2 & 30 & $1 \leq N, Q \leq 10^4$ \\ 
\hline
3 & 60 & No additional constraints. \\
\hline
\end{tabular}
\end{center}

\Example

\begin{example}
\exmpfile{example.01}{example.01.a}%
\end{example}

\Note
For the sample testcase:

At the beginning, the shirts are like so\\
($1$, $2$, $3$, $4$, $5$)\\
After the first query, (Change trainee $5$'s shirt to colour $4$)\\
($1$, $2$, $3$, $4$, $4$)\\
After the second query, (Change trainee $4$'s shirt to colour $2$)\\
($1$, $2$, $3$, $2$, $2$)\\
For the third query, output number of trainees wearing a shirt of colour 2\\
There are 3 students wearing a shirt of colour 2\\
After the fourth query, (Change trainee $3$'s shirt to colour $2$)\\
($1$, $2$, $2$, $2$, $2$)\\
After the fifth query, (Change trainee $2$'s shirt to colour $3$)\\
($1$, $3$, $3$, $3$, $3$)\\
For the sixth query, output number of trainees wearing a shirt of colour 3\\
There are 4 students wearing a shirt of colour 3\\

\end{problem}

