Legend:
The trainers at December Course 2024 are overwhelmed by the number of signups this year. With only a small number of trainers available, it's common to see trainers moving between labs. TheRaptor wants to monitor each trainer's movements to ensure no one is slacking off.

Trainers can move to a new lab $i$, and TheRaptor wants to know how many trainers are currently in lab $j$. Your task is to help TheRaptor answer these queries efficiently.

You will be given $q$ queries, which can be of two types:

    $1\ s\ i$: Trainer $s$ moves to lab $i$. Trainer $s$ may move back to the same lab or to a different one (To go to the toilet lol).
    
    $2\ j$: Output the number of trainers currently in lab $j$.

Input format:
The input is given in the following format:

$q$

$query_1$

$query_2$

$\vdots$

$query_q$

Each query is in one of the following formats:

$1\ s\ i$

$2\ j$

Where:

    $s$ is the name of the trainer (a string of lowercase English letters).
    $i$ and $j$ are integers representing lab indices.

Output format:
For each type $2$ query, output the number of trainers currently in lab $j$, each on a new line.

Scoring:
Scoring:
\begin{table}[h!]
    \begin{center}
        \begin{tabular}{|c|c|c|} 
            \hline
            \textbf{Subtask} & \textbf{Score} & \textbf{Additional constraints} \\
            \hline
            1 & 20 & $q \leq 100$, $i, j \leq 2$ \\
            \hline
            2 & 30 & $q \leq 10^3$, $i, j \leq 100$, number of trainers $\leq 10^3$ \\
            \hline
            3 & 50 & $q \leq 10^5$, $i, j \leq 10^5$, number of trainers $\leq 10^5$ \\
            \hline
        \end{tabular}
    \end{center}
\end{table}

Notes:
Given the input:

7  
1 alice 2  
1 bob 3  
2 2  
1 alice 3  
2 3  
1 charlie 3  
2 3  

The explanation is as follows:

    After the first query, trainer "alice" moves to lab 2.
    After the second query, trainer "bob" moves to lab 3.
    The third query asks for the number of trainers in lab 2. The result is $1$ ("alice").
    After the fourth query, trainer "alice" moves to lab 3.
    The fifth query asks for the number of trainers in lab 3. The result is $2$ ("bob" and "alice").
    After the sixth query, trainer "charlie" moves to lab 3.
    The seventh query asks for the number of trainers in lab 3. The result is $3$ ("bob", "alice", and "charlie").